---
title: "MultiGroupO vignette"
output: 
  rmarkdown::html_vignette:
    css: vignette.css
    toc: true
vignette: >
  %\VignetteIndexEntry{MultiGroupO vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  fig.width=6,
  fig.height=5,
  collapse = TRUE,
  comment = "#"
)

```

<style>
/*body {background-color: powderblue;}*/
h1   {color: blue;}
p    {color: black;}
</style>


<div class="top"><a class="toplink" href="#nav" title="&uArr; top">&nbsp;</a></div>
<div id="nav">
<ul>
<li>[vignetteMult](vignetteMult.html)</li>
<li>[datR](datR.html "Real Datasets Application")</li>
</ul>
</div>

# Introduction
The package contains functions to simulate multigroup data from a multivariate normal with different mean, matrix structures of variances and covariances, it will also consider not only biological signal but also considers noise variables for the different sizes of groups that can be balanced or unbalanced. It also contains functions with the new proposed multigroup methods. 

For an overview of supported, methods, and defaults together with some basic examples see

  * [README](https://cran.r-project.org) of the released version on CRAN;
  * [README](https://github.com) of the development version on GitHub.


# Installation
You can install the development version from [GitHub](https://github.com/) with
```
# install.packages("remotes")
remotes::install_github("carolina/MultiGroupO")
```
# Contributors
- Carolina Millapan (author, maintainer)
- Ferran Reverter (author)
- Esteban Vegas (author)
 

# Session Information

```{r setup}
library(MultiGroupO)
sim.list<-fun.sim(g=c(30,30,30),mean1=2,d=0,sds2=c(1,1,1,1),corr=c(0.5,0.5,0.5,0),
                      n.var=c(20,50))
    datos1 <- as.data.frame(sim.list$x)
    datos1<-subset(datos1,select=-grp)
    grupos <- sim.list$grp
     pca(datos1,grupos,Plot=TRUE,center=TRUE,scale=FALSE)
     mat.to.diag1<-new.cov(datos1,cls=grupos,A=diag(ncol(datos1)))
      mgpca(mat.to.diag=mat.to.diag1,mat.x=as.matrix(datos1),cls=grupos,Plot=T,ncomp=2,center = TRUE,scale = TRUE)
```

```{r setup2}
library(MultiGroupO)
sim.list<-fun.sim(g=c(30,30,30),mean1=2,d=0,sds2=c(1,1,1,1),corr=c(0.5,0.5,0.5,0),
                  n.var=c(20,50))
datos1 <- as.data.frame(sim.list$x)
datos1<-subset(datos1,select=-grp)
grupos <- sim.list$grp
mdr(group=grupos,data.x=sim.list$`lisx`,c=2)
```

